\textbf{WIP} \\

The Catalyst network allows nodes to be rewarded for storing data added to the DFS by other nodes on the network. These may include large files or complex data sets. The reason for payment for holding of data is to provide incentive for peers on the network to store data for others. The market place works as a method of pairing nodes who wish to store data with those that have excess space they wish to sell. By incentivising the process of storage of data on the ledger it can be ensured that when uploaded a file is persistent and accessible at all times. \\

One key issue for this marketplace is ensuring that those nodes that are claiming to store a particular element of data are in fact storing it. Furthermore, it needs to be ensured that these nodes are online are respond to requests for the data in a timely manor. In some situations this data may need to be checked with a high frequency, for others it may be a long term storage solution. It must also be ensured that a particular storage node does not already hold the information that it is being requested to store, as this will lead to the node being paid twice for storing the same item. \\

Catalyst network utilises the Proof of Replication (PoR) and Proof of Space Time (PoST) mechanisms laid out by Filecoin \cite{benet2018filecoin}. Furthermore, through the use of the 0x protocol \cite{warren20170x} so all storage purchase requests can be settled on chain.  \\

PoR allows a storage node to prove to another peer on the network that a file given to it has been replicated and is unique. This means that this individual piece of data has been copied by the storage node and is held in a unique compartment of physical storage, \textit{i.e.} that this is the first time this node has been asked to store this file and they are not getting paid twice for storing one file. This is important as the node storing the data on the DFS may (and in all likelihood will) want to store the data across multiple nodes to prevent a single point of failure. PoR prevents the storage node accepting multiple bids from the node storing their file on the DFS and taking multiple rewards for it. \\

PoST is an audit process for the storage nodes. It allows the creation of a challenge, the response to this challenge from a storage node allows it to demonstrate that it has stored the data required of it and furthermore that it is consistently storing the data without the need to repeatedly require it to present the data. 